A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-05-15 paper.Rmd
condense data sharing in julia and python section

## Challenges

**Challenges: higher potential impact means more time**

@@

Sharing data in a programming language happens to some extent in other languages. We discuss how Julia and Python share and distribute data in the following section.

# Julia

Julia was established in 2012, and is a high level language with great performance. Searching METADATA.jl [@METADATA-jl] for packages mentioning data revealed three main categories of data packages in Julia:

1. Database access [@data-access] for services like MySQL, Hive, and ODBC, similar to R’s DBI organization [@R-DBI]
2. Accessing data online via APIs, such as accessing the weather source NOAA [@NOAA-jl]
3. Data is provided directly. For example, accessing Econometric datasets [@econ-data-jl], face datasets [@face-data-jl], Market data [@market-data-jl], and even R datasets [@r-data-jl]. It is telling that the datasets provided in R are useful, as there is even a Julia package, RDatasets that provides over 700 datasets from R packages. There are also packages for Accessing datasets used in vega [@vega-data-jl], for accessing common machine learning datasets [@ml-data-jl]. There are also packages for generating fake data [@fake-data-jl], for which there are at least two R packages that do this, charlatan [@charlatan-data-r], and [@wakefield-data-r].

# Python

Python is a popular general purpose language, used in engineering, statistics, and computer science. One language agnostic solution is to use the Open Knowledge Foundations Frictionless data spec. This is implemented in both R and Python.

Including data in a python package: [@include-data-py-pkg]
A user can typically include data (or any other arbitrary files) inside a python package by declaring it in the manifest.

@@

>>>>

## Higher potential impact means more time**

@@

Sharing data in a programming language happens to some extent in other languages, such as Julia and Python.

Julia was established in 2012, and is a high level language with great performance.
Similar to R, Julia provides packages for database access, API access, and data packages [@METADATA-jl]. This includes access to MySQL databases, NOAA [@NOAA-jl], and actual datasets from Econometrics [@econ-data-jl], faces, [@face-data-jl], Market data [@market-data-jl], and even R datasets [@r-data-jl].

Python is a popular general purpose language, used in engineering, statistics, and computer science. 
Including data in a python package is straightforward; a user can include data (or any other arbitrary files) inside a python package by declaring it in the manifest [@include-data-py-pkg].

@@

# Morgue

One language agnostic solution is to use the Open Knowledge Foundations Frictionless data spec, implemented in both R and Python.
